---
title: "Experiment3_Memorability"
author: "RF"
date: "8/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

About data cleaning:
- If we need to combine the logfiles and the imageSimilarity data, then we would have to pair them based on participant ID and stim. So, the logfile column ID needs to match the similarity column ID, and the logfile column Stimulus needs to match the similarity column Master (possibly the screenshot column also needs to match the copy column).
1) Rename "master" to "stimulus".
2) cbind the two df's (make sure to have same number of observations).
3) Remove outliers (at least images that are completely white where the participant clicked before they got to reproduce the pattern).



## Load file and data

```{r cars}
pacman::p_load(tidyverse,brms,ggbeeswarm)

#######################################################
filePaths3 <- list.files("data/logfiles-memorability/", "\\.csv$", full.names = TRUE)
logfiles <- do.call(rbind, lapply(filePaths3, read.csv))
imgSim <- read_csv("data/ImageSimilarityData.csv")
# Logfile 40 is excluded, because it for some reason is not in the imgSim data.

imgSim <- imgSim %>% rename(
  Stimulus = drawing,
  TimeStamp = time
)

table(imgSim$ID)     #All id's in the imgSim data have one more observation. Perhaps the practice trial was screenshotted as well?
table(logfiles$ID)

# Now, after Kristian remade the MSR values, they have been dublicated, so we have to remove the reoccuring rows of copy name
imgSim <- imgSim[!duplicated(imgSim$copy),]

class(logfiles$ID)
imgSim$ID <- as.integer(imgSim$ID)

dfm <- merge(logfiles, imgSim, by = c("ID", "Stimulus"))

table(dfm$ID) #I can see that the rows that didn't have a match have been omitted, which is good.

class(dfm$ID)
dfm$ID <- as.factor(dfm$ID)
dfm$Orientation <- as.factor(dfm$Orientation)

dfm$X1 <- NULL
dfm$Screenshot_name <- NULL
dfm$TimeStamp.y <- NULL

# remove the trials where the participants clicked before recreating any pattern
dfm <- dfm[dfm$copy != "stimulus_o1_b1_c2_n3_034_2021_Nov_09_1330" & 
                  dfm$copy != "stimulus_o1_b1_c3_n2_009_2021_Oct_28_1621" &
                   dfm$copy != "stimulus_o1_b3_c1_n2_014_2021_Oct_29_0932" &
                   dfm$copy != "stimulus_o1_b3_c1_n2_020_2021_Nov_01_0834" &
                   dfm$copy != "stimulus_o1_b3_c3_n1_034_2021_Nov_09_1331", ] 

#######################################################

# Option 1
dfm$Complexity_ordered <- ordered(dfm$Complexity)
dfm$Noise_ordered <- ordered(dfm$Noise)
dfm$BlankSpace_ordered <- ordered(dfm$BlankSpace)

# Option 2
class(dfm$Complexity) #integer
dfm$Complexity_numeric <- factor(dfm$Complexity, levels = c("1", "2", "3"))
dfm$Complexity_numeric <- as.numeric(dfm$Complexity)
dfm$Complexity_numeric <- dfm$Complexity_numeric - 2

dfm$Noise_numeric <- as.numeric(dfm$Noise)
dfm$Noise_numeric <- dfm$Noise_numeric - 2
dfm$BlankSpace_numeric <- as.numeric(dfm$BlankSpace)
dfm$BlankSpace_numeric <- dfm$BlankSpace_numeric - 2


# Option 1: Transform MSE so that it is on a 0-1 scale
dfm$MSE_1 = dfm$MSE - min(dfm$MSE)
dfm$MSE_1 = dfm$MSE / max(dfm$MSE)

# Option 2: Standardize
pacman::p_load(rethinking)
dfm$MSE_2 = standardize(dfm$MSE)

```

## Run analyses

Outcome variable options:
 - pure MSE
 - transformed
 - standardized
Random effects options:
 - With / without orientation (xxx orientation as a fixed effect?)
predictor variable options:
 - Ordered
 - Numeric (as in the 2020 study)

```{r}
CHAINS = 2
ITER = 4000
CONTROLS = list(
  max_treedepth = 20,
  adapt_delta=0.999
  )

f1 <- bf(MSE ~ 1 + Complexity_ordered)

get_prior(m1, dfm) #What am I supposed to make of this??xxx

prior <- c(
  prior(normal(0,.3), class = Intercept), #xxx help
  prior(normal(0,.1), class = b),
  prior(normal(0,.05), class = sd)
)

m1_prior <- brm(f1,
             data = dfm,
             family = gaussian,
             prior = prior,
             sample_prior = "only",
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS
             )
```



# 1. Numeric vs ordered models. Transformed MSE (option 1)
```{r ordered - complexity}

m_c_f1 <- bf(MSE_1 ~ 1 + Complexity_numeric + (1 + Complexity_numeric | ID) + (1 | Stimulus) + (1 | Orientation))
m_c_f1_q <- bf(MSE_1 ~ 1 + Complexity_numeric + I(Complexity_numeric)^2 
               (1 + Complexity_numeric + I(Complexity_numeric)^2 | ID) + 
                 (1 | Stimulus) + 
                 (1 | Orientation)) #model comparison

m_c_f2 <- bf(MSE_1 ~ 1 + Complexity_ordered + (1 + Complexity_ordered | ID) + (1 | Stimulus) + (1 | Orientation)) #!!! is the orientation error due to the crop from rectangular to quadratic? Maybe just ignore it? bring it up in the discussion briefly. beyond the scope of this study. Interaction model could be made and compared to the pure complexity model.
m_c_f2.1 <- bf(MSE_1 ~ 1 + Complexity_ordered + (1 + Complexity_ordered | ID) + (1 | Stimulus)) # <- This is probably the one:))
m_c_f2.2 <- bf(MSE_1 ~ 1 + Complexity_ordered * Orientation + (1 + Complexity_ordered | ID) + (1 | Stimulus)) 

get_prior(m_c_f1, dfm)
get_prior(m_c_f2.1, dfm)

m_c_prior1 <- c(
  prior(normal(0,.3), class = Intercept),   #xxx are these priors wrong? because in the pp_check it seems that the samples are centered around 0, but the dark blue line is not..?
  prior(normal(0,.1), class = b),
  prior(normal(0,.05), class = sd),
  prior(lkj(5), class = cor)
)
m_c_prior1.0 <- c(
  prior(normal(0,.3), class = Intercept), 
  prior(normal(0,.1), class = b),
  prior(normal(0,.05), class = sd),
  prior(lkj(1), class = cor)   # xxx I am not sure what the diff is, so we'll run with 5. Don't remember why.
)

#Prior model
m_c_m1_prior <- brm(m_c_f2.1,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = "only",
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS
             )
m_c_m1.0_prior <- brm(m_c_f1,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1.0,
             sample_prior = "only",
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS
             )
m_c_m2_prior <- brm(m_c_f2,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = "only",
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS
             )

# prior predictive check
pp_check(m_c_m2.1_prior, nsamples=30) #the dark blue line has a very high peak compares to the samples. xxx
y_pred_c_m1 <- posterior_linpred(m_c_m1_prior)
dens(inv_logit(y_pred_c_m1)) # looks at the density now. Almost uniform distribution discounting extremes. (xxx ???)

pp_check(m_c_m2_prior, nsamples=100)
y_pred_c_m2 <- posterior_linpred(m_c_m2_prior)
dens(inv_logit(y_pred_c_m2))


# Real model
m_c_m1 <- brm(m_c_f1,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_c_m1"
             )
#m_c_m1 <- add_ic(m_c_m1,ic="LOO",cores=2)

m_c_m1_q <- brm(m_c_f1,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_c_m1_q"
             )

m_c_m2 <- brm(m_c_f2,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_c_m2"
             )
#m_c_m2 <- add_ic(m_c_m2,ic="LOO",cores=2)

m_c_m2.1 <- brm(m_c_f2.1,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_c_m2.1"
             )
#m_c_m2.1 <- add_ic(m_c_m2.1,ic="LOO",cores=2)

m_c_m2.2 <- brm(m_c_f2.2,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_c_m2.2"
             )
#m_c_m2.2 <- add_ic(m_c_m2.2,ic="LOO",cores=2)


print(summary(m_c_m1))
print(marginal_effects(m_c_m1))
print(hypothesis(m_c_m1, "Complexity_numeric < 0", class = "b"))
plot(hypothesis(m_c_m1, "Complexity_numeric < 0", class = "b"))

print(summary(m_c_m1_q))
print(marginal_effects(m_c_m1_q))
print(hypothesis(m_c_m1_q, "Complexity_numeric < 0", class = "b"))
plot(hypothesis(m_c_m1_q, "Complexity_numeric < 0", class = "b"))

print(summary(m_c_m2))
print(marginal_effects(m_c_m2))
print(hypothesis(m_c_m2, "Complexity_ordered.L < 0", class = "b"))
print(hypothesis(m_c_m2, "Complexity_ordered.Q < 0", class = "b"))
plot(hypothesis(m_c_m2, "Complexity_ordered.L < 0", class = "b"))
plot(hypothesis(m_c_m2, "Complexity_ordered.Q < 0", class = "b"))

print(summary(m_c_m2.1))
print(marginal_effects(m_c_m2.1))
print(hypothesis(m_c_m2.1, "Complexity_ordered.L > 0", class = "b"))
print(hypothesis(m_c_m2.1, "Complexity_ordered.Q > 0", class = "b"))
plot(hypothesis(m_c_m2.1, "Complexity_ordered.L > 0", class = "b"))
plot(hypothesis(m_c_m2.1, "Complexity_ordered.Q > 0", class = "b"))

print(summary(m_c_m2.2))
print(marginal_effects(m_c_m2))
print(hypothesis(m_c_m2.2, "Complexity_ordered.L < 0", class = "b"))
print(hypothesis(m_c_m2.2, "Complexity_ordered.Q < 0", class = "b"))
plot(hypothesis(m_c_m2.2, "Complexity_ordered.L < 0", class = "b"))
plot(hypothesis(m_c_m2.2, "Complexity_ordered.Q < 0", class = "b")) #xxx why do I get an evidence ratio of zero even though the plots seem to show pretty significant effects??
```



# Noise
```{r Noise models}

m_n_f1 <- bf(MSE_1 ~ 1 + Noise_numeric + (1 + Noise_numeric | ID) + (1 | Stimulus) + (1 | Orientation))
m_n_f1_q <- bf(MSE_1 ~ 1 + Noise_numeric + I(Noise_numeric)^2 
               (1 + Noise_numeric + I(Noise_numeric)^2 | ID) + 
                 (1 | Stimulus) + 
                 (1 | Orientation))

m_n_f2 <- bf(MSE_1 ~ 1 + Noise_ordered + (1 + Noise_ordered | ID) + (1 | Stimulus) + (1 | Orientation)) 
m_n_f2.1 <- bf(MSE_1 ~ 1 + Noise_ordered + (1 + Noise_ordered | ID) + (1 | Stimulus)) 
m_n_f2.2 <- bf(MSE_1 ~ 1 + Noise_ordered * Orientation + (1 + Noise_ordered | ID) + (1 | Stimulus)) 

m_n_prior1 <- c(
  prior(normal(0,.3), class = Intercept),
  prior(normal(0,.1), class = b),
  prior(normal(0,.05), class = sd),
  prior(lkj(5), class = cor)
)

# model
m_n_m1 <- brm(m_n_f1,
             data = dfm,
             family = gaussian,
             prior = m_n_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_n_m1"
             )

m_n_m1_q <- brm(m_n_f1,
             data = dfm,
             family = gaussian,
             prior = m_n_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_n_m1_q"
             )

m_n_m2 <- brm(m_n_f2,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_n_m2"
             )

m_n_m2.1 <- brm(m_n_f2.1,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_n_m2.1"
             )

m_n_m2.2 <- brm(m_n_f2.2,
             data = dfm,
             family = gaussian,
             prior = m_c_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_n_m2.2"
             )

print(summary(m_n_m1))
print(marginal_effects(m_n_m1))
print(hypothesis(m_n_m1, "Noise_numeric < 0", class = "b"))
plot(hypothesis(m_n_m1, "Noise_numeric < 0", class = "b"))

print(summary(m_n_m1_q))
print(marginal_effects(m_n_m1_q))
print(hypothesis(m_n_m1_q, "Noise_numeric < 0", class = "b"))
plot(hypothesis(m_n_m1_q, "Noise_numeric < 0", class = "b"))

print(summary(m_n_m2))
print(marginal_effects(m_n_m2))
print(hypothesis(m_n_m2, "Noise_ordered.L < 0", class = "b"))
print(hypothesis(m_n_m2, "Noise_ordered.Q < 0", class = "b"))
plot(hypothesis(m_n_m2, "Noise_ordered.L < 0", class = "b"))
plot(hypothesis(m_n_m2, "Noise_ordered.Q < 0", class = "b"))

print(summary(m_n_m2.1))
print(marginal_effects(m_n_m2.1))
print(hypothesis(m_n_m2.1, "Noise_ordered.L > 0", class = "b"))
print(hypothesis(m_n_m2.1, "Noise_ordered.Q > 0", class = "b"))
plot(hypothesis(m_n_m2.1, "Noise_ordered.L > 0", class = "b"))
plot(hypothesis(m_n_m2.1, "Noise_ordered.Q > 0", class = "b"))

print(summary(m_n_m2.2))
print(marginal_effects(m_n_m2))
print(hypothesis(m_n_m2.2, "Noise_ordered.L < 0", class = "b"))
print(hypothesis(m_n_m2.2, "Noise_ordered.Q < 0", class = "b"))
plot(hypothesis(m_n_m2.2, "Noise_ordered.L < 0", class = "b"))
plot(hypothesis(m_n_m2.2, "Noise_ordered.Q < 0", class = "b"))
```


# Blank Space
```{r Blank Space models}
m_b_f1 <- bf(MSE_1 ~ 1 + BlankSpace_numeric + (1 + BlankSpace_numeric | ID) + (1 | Stimulus) + (1 | Orientation))
m_b_f1_q <- bf(MSE_1 ~ 1 + BlankSpace_numeric + I(BlankSpace_numeric)^2 
               (1 + BlankSpace_numeric + I(BlankSpace_numeric)^2 | ID) + 
                 (1 | Stimulus) + 
                 (1 | Orientation))

m_b_f2 <- bf(MSE_1 ~ 1 + BlankSpace_ordered + (1 + BlankSpace_ordered | ID) + (1 | Stimulus) + (1 | Orientation)) 
m_b_f2.1 <- bf(MSE_1 ~ 1 + BlankSpace_ordered + (1 + BlankSpace_ordered | ID) + (1 | Stimulus)) 
m_b_f2.2 <- bf(MSE_1 ~ 1 + BlankSpace_ordered * Orientation + (1 + BlankSpace_ordered | ID) + (1 | Stimulus)) 

m_b_prior1 <- c(
  prior(normal(0,.3), class = Intercept),
  prior(normal(0,.1), class = b),
  prior(normal(0,.05), class = sd),
  prior(lkj(5), class = cor)
)

# model
m_b_m1 <- brm(m_b_f1,
             data = dfm,
             family = gaussian,
             prior = m_b_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_b_m1"
             )

m_b_m1_q <- brm(m_b_f1,
             data = dfm,
             family = gaussian,
             prior = m_b_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_b_m1_q"
             )

m_b_m2 <- brm(m_b_f2,
             data = dfm,
             family = gaussian,
             prior = m_b_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_b_m2"
             )

m_b_m2.1 <- brm(m_b_f2.1,
             data = dfm,
             family = gaussian,
             prior = m_b_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_b_m2.1"
             )

m_b_m2.2 <- brm(m_b_f2.2,
             data = dfm,
             family = gaussian,
             prior = m_b_prior1,
             sample_prior = TRUE,
                   chains = CHAINS,cores=CHAINS,
                   iter = ITER,
                   control = CONTROLS,
             file = "models/memorability/m_b_m2.2"
             )

print(summary(m_b_m1))
print(marginal_effects(m_b_m1))
print(hypothesis(m_b_m1, "BlankSpace_numeric < 0", class = "b"))
plot(hypothesis(m_b_m1, "BlankSpace_numeric < 0", class = "b"))

print(summary(m_b_m1_q))
print(marginal_effects(m_b_m1_q))
print(hypothesis(m_b_m1_q, "BlankSpace_numeric < 0", class = "b"))
plot(hypothesis(m_b_m1_q, "BlankSpace_numeric < 0", class = "b"))

print(summary(m_b_m2))
print(marginal_effects(m_b_m2))
print(hypothesis(m_b_m2, "BlankSpace_ordered.L < 0", class = "b"))
print(hypothesis(m_b_m2, "BlankSpace_ordered.Q < 0", class = "b"))
plot(hypothesis(m_b_m2, "BlankSpace_ordered.L < 0", class = "b"))
plot(hypothesis(m_b_m2, "BlankSpace_ordered.Q < 0", class = "b"))

print(summary(m_b_m2.1))
print(marginal_effects(m_b_m2.1))
print(hypothesis(m_b_m2.1, "BlankSpace_ordered.L < 0", class = "b"))
print(hypothesis(m_b_m2.1, "BlankSpace_ordered.Q < 0", class = "b"))
plot(hypothesis(m_b_m2.1, "BlankSpace_ordered.L < 0", class = "b"))
plot(hypothesis(m_b_m2.1, "BlankSpace_ordered.Q < 0", class = "b"))
######
print(summary(m_b_m2.1))
print(marginal_effects(m_b_m2.1))
print(hypothesis(m_b_m2.1, "BlankSpace_ordered.L > 0", class = "b"))
print(hypothesis(m_b_m2.1, "BlankSpace_ordered.Q > 0", class = "b"))
plot(hypothesis(m_b_m2.1, "BlankSpace_ordered.L > 0", class = "b"))
plot(hypothesis(m_b_m2.1, "BlankSpace_ordered.Q > 0", class = "b"))


print(summary(m_b_m2.2))
print(marginal_effects(m_b_m2))
print(hypothesis(m_b_m2.2, "BlankSpace_ordered.L < 0", class = "b"))
print(hypothesis(m_b_m2.2, "BlankSpace_ordered.Q < 0", class = "b"))
plot(hypothesis(m_b_m2.2, "BlankSpace_ordered.L < 0", class = "b"))
plot(hypothesis(m_b_m2.2, "BlankSpace_ordered.Q < 0", class = "b"))
```





## Report the winning model
```{r}
# Model comparison
compare_ic(MSE_m1, MSE_m2,ic="loo")
model_weights(MSE_m1, MSE_m2,ic="loo")

# Summarizing and visualizing results
summary(MSE_m1)
hypothesis(MSE_m1,"PeriodL<0")
marginal_effects(MSE_m1)

pp_check(MSE_m1,nsamples=100)



```


## Plots

```{r}
## Plot for the main manuscript

dfm_agg_c <- subset(dfm) %>% group_by(ID, Complexity_ordered) %>% dplyr::summarize(
  meanError = mean(MSE,na.rm=T),
  )

dfm_agg_c$ID = as.factor(dfm_agg_c$ID)

Exp3_MainPlot <- ggplot(dfm_agg_c, aes(Complexity_ordered, meanError)) + 
  geom_line(aes(group = ID, color = ID), alpha = 0.3) +
  geom_point(aes(group = ID, color = ID), alpha = 0.3) +
  geom_smooth(method = lm) +  #where is the smooth? xxx
  theme_classic() +
  ylab("Average error in reproducing the stimulus") +
  xlab("Complexity") +
  scale_color_discrete(guide = FALSE) +
  #scale_x_continuous(breaks = c(1, 2, 3), labels = c("Low", "Medium", "High")) +
  NULL
Exp3_MainPlot
#ggsave("Exp3_MainPlot.svg", plot = Exp3_MainPlot)





# Plot for the supplemtary materials
ggplot(d, aes(PeriodL,MSE)) + 
  geom_beeswarm(aes(color=Site),alpha=0.5) + 
  theme_classic() + 
  geom_smooth(method=lm, alpha=0.8, color="gray50", fill="gray") +
  xlab("Period") +
  ylab("Normalized error in reproduction")+
  scale_x_continuous(breaks = c(-1,0,1),labels=c("Early","Intermediate","Late")) +
  NULL

ggsave("Plots/Exp3_MseDataPlot.svg",width = 10, height = 6)

ggplot(d, aes(PeriodL,MSE,color=Site)) + 
  geom_beeswarm(alpha=0.5) + 
  theme_classic() + 
  geom_smooth(method=lm, alpha=0.8) +
  xlab("Time") +
  ylab("Error in reproduction (scale 0-1)")

ggsave("Exp3_MseSiteDataPlot.svg",width = 23, height = 18)

```






```{r Kristians plots}

ggplot(dfm, aes(Complexity, MSE, color = Orientation)) + 
  geom_point() +
  geom_smooth(method = lm)

ggplot(dfm, aes(Noise, MSE, color = Orientation)) + 
  geom_point() +
  geom_smooth(method = lm)

ggplot(dfm, aes(BlankSpace, MSE, color = Orientation)) + 
  geom_point() +
  geom_smooth(method = lm)
```





