---
title: "Experiment1_TTE_Saliency"
author: "RF"
date: "8/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analyzing Experiment 1 - Time to Emerge is a function of period

### Load data and libraries

```{r Data and Libraries}

pacman::p_load(tidyverse,lmerTest,brms,fitdistrplus,ggbeeswarm,svglite)

d <- read_csv("Data/Exp1_TTE.csv")
d <- d %>% rename(RT = Reaction_time,Site = TargetSite)
d <- subset(d, RT > 0.2)
d$Correct <- as.factor(d$Correctness)
d <- subset(d,!is.na(Correct))
d$ID <- as.factor(d$ID)
d <- subset(d,ID!=66) # Excluding participant with all extremely low RTs 
d$PeriodL <- d$PeriodL - 2
dC <- subset(d,Correct==1)
dC$RT1 <- dC$RT/max(dC$RT)


CHAINS = 2
ITER = 8e3
CONTROLS = list(
  max_treedepth = 20,
  adapt_delta=0.999
  )
```

## Exploratory visualization

```{r Exploratory Visualization}
# Double-checking the RTs
ggplot(d,aes(Reaction_time)) + 
  geom_density(aes(fill=Correct,group=Correct,color=Correct),alpha=0.3) +
  facet_wrap(Type~Correct) +
  NULL

# It looks like a nice gamma, but there is a 0 second mode in correct = 0

## By participant
ggplot(d,aes(Reaction_time)) + 
  geom_density(aes(fill=ID,group=ID,color=ID),alpha=0.3) +
  facet_wrap(Type~Correct) +
  guides(fill=FALSE,group=FALSE,color=FALSE) +
  NULL

### Distribution analysis by participant
C1=subset(d,Correctness==1)
for (i in unique(d$ID)){
  x=C1$Reaction_time[C1$ID==i]
  fn <- fitdist(x, "norm")
  Normal=summary(fn)$aic
  fln <- fitdist(x, "lnorm")
  LogNormal=summary(fln)$aic
  fg <- fitdist(x, "gamma")
  Gamma=summary(fg)$aic
  x<- data.frame(ID=i,Normal,LogNormal,Gamma)
  if (exists("FitData")){FitData=rbind(FitData,x)}else{FitData=x}
}

C1 <- FitData %>% gather(Distribution, Fit, Normal:Gamma, na.rm = FALSE, convert = FALSE)

ggplot(C1,aes(Distribution,Fit)) +
  geom_violin() +
  geom_beeswarm(aes(color=Distribution))

# Definitely not normal, not super persuasive difference between lognormal and gamma
# Conceptual reflection says gamma

## Let's explore accuracy and rt by period

ggplot(d, aes(Correct)) +
  geom_bar(stat="count") + facet_wrap(.~Period)

ggplot(subset(d,Correct==1),aes(PeriodL,Reaction_time)) +
  geom_violin() +
  geom_beeswarm(aes(color=Period))

```

## Analysis proper

### Is accuracy affected by period? Signal Detection Theory model of accuracy

```{r}

AccuracySDT_f1 <- bf(Response ~ 1 + Correct_response * PeriodL + (1 + Correct_response * PeriodL | ID) + (1+ Correct_response | Drawing))
AccuracySDT_f2 <- bf(Response ~ 1 + Correct_response * (PeriodL + I(PeriodL)^2) + (1 + Correct_response * (PeriodL + I(PeriodL)^2) | ID) + (1+ Correct_response | Drawing))

AccuracySDT_prior <- c(
           prior(normal(0,1), class = Intercept),
           prior(normal(0,1), class = b),
           prior(normal(0,1), class = sd),
           prior(lkj(5),      class=cor))

AccuracySDT_m1 <- brm(AccuracySDT_f1,
                   family=bernoulli(link="probit"),
                   data=subset(d,Type=="Stimuli"),
                   prior=AccuracySDT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
AccuracySDT_m1 <- add_ic(AccuracySDT_m1,ic="LOO",cores=CHAINS)

AccuracySDT_m2 <- brm(AccuracySDT_f2,
                   family=bernoulli(link="probit"),
                   data=subset(d,Type=="Stimuli"),
                   prior=AccuracySDT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
AccuracySDT_m2 <- add_ic(AccuracySDT_m2,ic="LOO",cores=CHAINS)


save(AccuracySDT_m1,AccuracySDT_m2, file="Models/Exp1_AccuracySDT_Models")

# Model comparison
print(compare_ic(AccuracySDT_m1,AccuracySDT_m2,ic="loo"))

# Summarizing and visualizing results
print(summary(AccuracySDT_m1))
print(marginal_effects(AccuracySDT_m1))
print(hypothesis(AccuracySDT_m1, "Correct_responseright:PeriodL>0"))

```

### Is RT affected by period?

```{r}
# Models conditioning rate only
RT_f1 <- bf(RT ~ 1 + PeriodL + (1 + PeriodL | ID) + (1|Drawing))
RT_f2 <- bf(RT ~ 1 + PeriodL + I(PeriodL)^2 + (1 + PeriodL  + I(PeriodL)^2 |i| ID) + (1|Drawing))

# Models conditioning rate and shape
RT_f1a <- bf(RT ~ 1 + PeriodL + (1 + PeriodL | p | ID) + (1|Drawing),
             shape ~ 1 + PeriodL + (1 + PeriodL | p | ID))
RT_f2a <- bf(RT ~ 1 + PeriodL + I(PeriodL)^2 + (1 + PeriodL  + I(PeriodL)^2  | p | ID) + (1|Drawing),
             shape ~ 1 + PeriodL + I(PeriodL)^2 + (1 + PeriodL + I(PeriodL)^2 | p | ID))

RT_prior <- c(
           prior(normal(0, .3), class = Intercept),
           prior(normal(0, .1), class = b),
           prior(normal(0, .3), class = sd),
           prior(lkj(5),      class=cor))

RT_m1 <- brm(RT_f1,
                   family=Gamma(link="log"),
                   data=subset(dC,Type=="Stimuli"),
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_m1 <- add_ic(RT_m1,ic="loo",cores=CHAINS)

RT_m1a <- brm(RT_f1a,
                   family=Gamma(link="log"),
                   data=subset(dC,Type=="Stimuli"),
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_m1a <- add_ic(RT_m1a,ic="loo",cores=CHAINS)

RT_m2 <- brm(RT_f2,
                   family=Gamma(link="log"),
                   data=subset(dC,Type=="Stimuli"),
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_m2 <- add_ic(RT_m2,ic="loo",cores=CHAINS)

RT_m2a <- brm(RT_f2a,
                   family=Gamma(link="log"),
                   data=subset(dC,Type=="Stimuli"),
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER, refresh=10,
                   control = CONTROLS)
RT_m2a <- add_ic(RT_m2a,ic="loo",cores=CHAINS)


save(RT_m1,RT_m1a,RT_m2,RT_m2a,file="Models/Exp1_RT_Models")

# Model comparison
print(compare_ic(RT_m1,RT_m1a,RT_m2,ic="loo"))
# Summarizing and visualizing results
print(summary(RT_m1a))
print(marginal_effects(RT_m1a))
print(hypothesis(RT_m1a, "PeriodL<0"))
```

### Plots of the RT findings

```{r}
## Plot for the main manuscript - Figure N
dC_agg<-dC %>% group_by(ID, PeriodL,Type) %>% dplyr::summarize(
  mRT = mean(RT,na.rm=T),
  sdRT = sd(RT,na.rm=T),
  mRT_log = mean(log(RT),na.rm=T),
  sdRT_log = sd(log(RT),na.rm=T))

Exp1_MainPlot <- ggplot(subset(dC_agg, Type=="Stimuli" & mRT_log>0),aes(PeriodL,mRT)) + 
  geom_line(aes(group=ID,color=ID),alpha=0.3) +
  geom_point(aes(group=ID,color=ID),alpha=0.3)+
  geom_smooth(method=lm) +
  theme_classic() +
  ylab("Time to emerge (seconds)") +
  xlab("Period") +
  scale_color_discrete(guide=FALSE) +
  scale_x_continuous(breaks = c(-1,0,1),labels=c("Early","Intermediate","Late")) +
  NULL
ggsave("Plots/Exp1_MainPlot.svg", plot = Exp1_MainPlot)


## Plot for the supplementary materials
ggplot(subset(dC, Type=="Stimuli"),aes(PeriodL,RT)) + 
  geom_beeswarm(aes(color=Site),alpha=0.3) + 
  geom_smooth(method=lm) +
  theme_classic() +
  ylab("Time to emerge (seconds)") +
  xlab("Period") +
  scale_x_continuous(breaks = c(-1,0,1),labels=c("Early","Intermediate","Late")) +
  NULL

ggsave("Plots/Exp1_RT_Stimuli.svg", width = 10)
```


### Control analysis for Type. Do originals show different effects? SDT and Gamma analyses

```{r}
AccuracySDT_Type_f0 <- bf(Response ~ 1 + Correct_response * PeriodL + Type + (1 + Correct_response * PeriodL + Type | ID) + (1+ Correct_response | Drawing))
AccuracySDT_Type_f1 <- bf(Response ~ 1 + Correct_response * PeriodL * Type + (1 + Correct_response * PeriodL * Type | ID) + (1+ Correct_response | Drawing))

AccuracySDT_Type_m0 <- brm(AccuracySDT_Type_f0,
                   family=bernoulli(link=probit),
                   data=d,
                   prior=AccuracySDT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
AccuracySDT_Type_m0 <- add_ic(AccuracySDT_Type_m0,ic="LOO",cores=CHAINS)

AccuracySDT_Type_m1 <- brm(AccuracySDT_Type_f1,
                   family=bernoulli(link=probit),
                   data=d,
                   prior=AccuracySDT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
AccuracySDT_Type_m1 <- add_ic(AccuracySDT_Type_m1,ic="LOO",cores=CHAINS)

# Model comparison
print(compare_ic(AccuracySDT_m1,AccuracySDT_Type_m0,AccuracySDT_Type_m1,ic="loo"))
save(AccuracySDT_Type_m0,AccuracySDT_Type_m1, file="Models/Exp1_Accuracy_Type")

# RT control analysis
RT_Type_f0 <- bf(RT ~ 1 + PeriodL + Type + (1 + PeriodL + Type | p | ID) + (1|Drawing),
             shape ~ 1 + PeriodL + Type + (1 + PeriodL + Type | p | ID))

RT_Type_f1 <- bf(RT ~ 1 + PeriodL * Type + (1 + PeriodL + Type | p | ID) + (1|Drawing),
             shape ~ 1 + PeriodL * Type + (1 + PeriodL * Type | p | ID))

RT_Type_m0 <- brm(RT_Type_f0,
                   family=Gamma(link="log"),
                   data=dC,
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_Type_m0 <- add_ic(RT_Type_m0,ic="LOO",cores=CHAINS)
save(RT_Type_m0, file="Models/Exp1_RT_Type")

RT_Type_m1 <- brm(RT_Type_f1,
                   family=Gamma(link="log"),
                   data=dC,
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_Type_m1 <- add_ic(RT_Type_m1,ic="LOO",cores=CHAINS)
save(RT_Type_m0,RT_Type_m1, file="Models/Exp1_RT_Type")

# Model comparison
print(compare_ic(RT_Type_m0,RT_Type_m1,ic="loo"))

# Visualizing differences in RT due to rate and shape differences between types

x1 <- rgamma(100000, shape = 2.03, rate = 0.66)
x2 <- rgamma(100000, shape = 2.03-0.29, rate = 0.66+0.04)

den1 <- density(x1)
den2 <- density(x2)

dat1 <- data.frame(x = den1$x, y = den1$y, Type="Originals")
dat2 <- data.frame(x = den2$x, y = den2$y, Type="Stimuli")
dat <- rbind(dat1,dat2)

# Plot density as points
ggplot(data = dat, aes(x = x, y = y, color=Type)) + 
  geom_point(size = 3) +
  theme_classic()

ggsave("Plots/Exp1_RT_TypeCheck.svg", width = 10)
```


## Control analysis for Site. Do different sites show different effects?
```{r}

dC <- dC %>% rename(Site=TargetSite) 
AccuracySDT_Site_f0 <- bf(Response ~ 1 + Correct_response * PeriodL + Site + (1 + Correct_response * PeriodL + Site | ID) + (1|Drawing))
AccuracySDT_Site_f1 <- bf(Response ~ 1 + Correct_response * PeriodL * Site + (1 + Correct_response * PeriodL * Site | ID) + (1|Drawing))

AccuracySDT_Site_m0 <- brm(AccuracySDT_Site_f0,
                   family=bernoulli(link=probit),
                   data=subset(d,Type=="Stimuli"),
                   prior=AccuracySDT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
AccuracySDT_Site_m0 <- add_ic(AccuracySDT_Site_m0,ic="LOO",cores=CHAINS)

AccuracySDT_Site_m1 <- brm(AccuracySDT_Site_f1,
                   family=bernoulli(link=probit),
                   data=subset(d,Type=="Stimuli"),
                   prior=AccuracySDT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
AccuracySDT_Site_m1 <- add_ic(AccuracySDT_Site_m1,ic="LOO",cores=CHAINS)

# Model comparison
compare_ic(AccuracySDT_Site_m0,AccuracySDT_Site_m1,ic="loo")
save(AccuracySDT_Site_m0,AccuracySDT_Site_m1, file="Models/Exp1_Accuracy_Site")

# Summarizing and visualizing results

# RT control analysis

RT_Site_f0 <- bf(RT ~ 1 + PeriodL + Site + (1 + PeriodL + Site | p | ID) + (1|Drawing),
             shape ~ 1 + PeriodL + Site + (1 + PeriodL + Site | p | ID))

RT_Site_f1 <- bf(RT ~ 1 + PeriodL * Site + (1 + PeriodL * Site | p | ID) + (1|Drawing),
             shape ~ 1 + PeriodL * Site + (1 + PeriodL * Site | p | ID))

RT_Site_m0 <- brm(RT_Site_f0,
                   family=Gamma(link="log"),
                   data=subset(dC,Type=="Stimuli"),
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_Site_m0 <- add_ic(RT_Site_m0,ic="LOO",cores=CHAINS)
save(RT_Site_m0,file="Models/Exp1_RT_Site")

RT_Site_m1 <- brm(RT_Site_f1,
                   family=Gamma(link="log"),
                   data=subset(dC,Type=="Stimuli"),
                   prior=RT_prior,
                   sample_prior=TRUE,
                   chains=CHAINS,cores=CHAINS,
                   iter=ITER,
                   control = CONTROLS)
RT_Site_m1 <- add_ic(RT_Site_m1,ic="LOO",cores=CHAINS)
save(RT_Site_m0,RT_Site_m1, file="Models/Exp1_RT_Site")

# Model comparison
print(compare_ic(RT_m1a,RT_Site_m0,RT_Site_m1,ic="loo"))

# Summarizing and visualizing results
print(summary(RT_Site_m1))
print(hypothesis(RT_Site_m1,"SiteDiepkloof<0"))
print(hypothesis(RT_Site_m1,"shape_SiteDiepkloof<0"))
print(hypothesis(RT_Site_m1,"PeriodL:SiteDiepkloof<0"))
print(hypothesis(RT_Site_m1,"shape_PeriodL:SiteDiepkloof<0"))
```

